---
title: "Comparing Groups"
---

```{r setup, include=FALSE}
# Delete stuff from directory
unlink(c("dataActive.csv", "rWestern.dta"))
```

# Authoritarianism scores by Ethnicity

This is how I load the data.

```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(dplyr)
library(rstan)
library(tidyr)
library(modelr)
library(brms)
library(tidybayes)
library(ggplot2)
library(simplecolors)
library(patchwork)
library(fastDummies)
library(bayesplot)
library(cowplot)
library(googleCloudStorageR)

# Data
load("~/Dropbox/github_repos/westAuthoritarianism/westernAuthoritarianism/tmp/modelsR.rda")
gcs_get_object("dataActive.csv", bucket = "grau_data", saveToDisk = "dataActive.csv", overwrite = TRUE)

modDat <- read.csv("dataActive.csv") %>%
  mutate(gen = factor(gen)) %>%
  dummy_cols(select_columns = "gen") %>%
  filter(race == "White" | race == "Hispanic") %>%
  mutate(authSum = rowMeans(cbind(auth1, auth2, auth3, auth4), na.rm = TRUE)) %>%
  mutate(authSum = zero.one(authSum)) %>%
  mutate(authM1 = zero.one(m1.dif)) %>%
  mutate(authM2 = zero.one(m2.dif)) %>%
  mutate(authM3 = zero.one(mean_name)) 
head(modDat)
```

## Data Description

The first file is just the cleaned western data. The second is the regression models. The third is a list of latent variable models.

```{r pressure, echo=FALSE, warning=FALSE, message=FALSE}

# Data 
 dat = modDat %>%
      data_grid(
                female  =  mean(female),
                college =  mean(college),
                income  =  mean(income),
                latino =   c(0, 1),
                married =  mean(married),
                christian     =  mean(christian),
                gen_Boomer    = mean(gen_Boomer),
                gen_Greatest  = mean(gen_Greatest),
                gen_Millenial = mean(gen_Millenial),
               authM3 = c(0,1))  %>%
      add_epred_draws(regressionModels[[1]]) %>%
      group_by(authM3, latino, .category) %>%
      mutate(latino = as.factor(ifelse(latino == 1, "Latino", "Non Hispanic White"))) %>%
      pivot_wider(names_from = .category, values_from = .epred, names_prefix = "cat_") 
head(dat)
```

These are the data reshaped in "wide" format to place the categories on the columns. Each entry refers to the probability that the simulated response lists this category as the most important. The data are grouped by the level of the moderator variable, Latino, and the level of the independent variable, authoritarianism.

From here -- in a rather unconcise way -- generate plotDat, which is the mean marginal effect of the moderator variable, Latino, on the probability that the category is the most important. Then from these data, extract the necessary variables to calculate the marginal effect. The marginal effect is the difference in the probability that the category is the most important for the two levels of the moderator variable.

Finally plot these effects


```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 6}        

plotDat =   dat %>%
  filter(authM3 == 1) %>%
  select(starts_with("cat") | latino) %>%
  pivot_longer(
    cols = starts_with("cat"),
    names_to = "category",
    values_to = "probability"
  ) 

maxX = plotDat %>%
  subset(select = "probability")

minX = dat %>%
  filter(authM3 == 0) %>%
  select(starts_with("cat")| latino) %>%
  pivot_longer(
    cols = starts_with("cat"),
    names_to = "category",
    values_to = "probability"
  ) %>% 
  subset(select = "probability")

plot =  plotDat %>% 
  select(latino, category) 

plot$marginal_effect = maxX$probability - minX$probability

plot = plot %>% 
  group_by(latino, category) %>% 
  summarize(
    mean = mean(marginal_effect),
    lower = quantile(marginal_effect, 0.025),
    upper = quantile(marginal_effect, 0.975)
  )

head(plot)
```
```{r}
# Width height
options(repr.plot.width = 12, repr.plot.height = 6)
plot = plot %>%
  ggplot(
    aes(
      x = reorder(factor(category), mean),
      y = mean, ymin = lower,
      ymax = upper, group = latino, color = latino
    )
  ) +
  geom_point(size = 2, position = position_dodge(width = 0.5), alpha = 0.75) +
  geom_errorbar(width = 0.15, position = position_dodge(width = 0.5), alpha = 0.75, colour = "black") +
  ggtitle("Marginal Effect of Authoritarianism") +
  scale_y_continuous("Marginal Effect", limits = c(-0.5, 0.5)) +
  geom_hline(yintercept = 0, colour = "black", linetype = "dashed") +
  coord_flip() + 
  # Change x axis to labels minus cat_ using a regex and upper case the first letter in the label
  scale_x_discrete("Most Important Problem", labels =  stringr::str_to_title(gsub("cat_", "",         levels(factor(plot$category))))) +
  theme(panel.background = element_rect(fill = "white")) +
  # Add a caption
  labs(caption = "Data come from the 2020 Western States Survey") +
  #Change color to ua_color_qualitative
  scale_color_manual("", values = c("#E63946", "#457B9D"))

plot

```
There are some notable differences between Latinos and non Hispanic Whites with respect to the political expression of authoritarian values. The marginal effect of authoritarianism on stating that "Policing" is the most important problem is greater for non Hispanic Whites. Non Hispanic White Authoritarians and non-authoritarians differ on this item. There is a non-significant difference among Latinos.

Negative values indicate that non-authoritarians rate the issue as more important, compared to authoritarians. There is a rather larger divide on "Covid" indicating that non-authoritarians are far more likely to rate the Covid pandemic as the most important problem. This effect is greater for non Hispanic Whites -- though the confidence regions overlap.   

While authoritarians and non authoritarians differ in important ways -- authoritarians are more likely to rate issues like foreign trade and police/law and order as the most important problem; non-authoritarians rate Covid and the economy as more important. The differences between Latinos and non Hispanic Whites with respect to the expression of authoritarian values, however, is less clear. 

We see some differences in the expression of authoritarian values across these groups. The authoritarian divide on the policing issue is more pronounced for non Hispanic Whites. The authoritarian divide on the economy is more pronounced for Latinos. Yet, what's important to note is that the marginal effect of authoritarianism is generally quite similar across these groups. The confidence region for the marginal effect of authoritarianism overlaps for these groups.

## The Expression of Authoritarian Values on Policy

The formula for all the regression models is:

```{r}
IV <- "female + latino + college + income + gen_Boomer + gen_Greatest +
       gen_Millenial +  married + christian +  authM3 + authM3:latino"
```

And then depending on the nature of the dependent variable, a multinomial, ordinal, or binary model is used, the logit link used for the latter two, softmax for the first.

Here is an example of a multinomial model. Let's predict partisanship with authoritarianism, and these variables. 

```{r}
regressionModels$pid3
```

Estimate the posterior means for the model. 

```{r}
xvar = "authM3"
mvar = "latino"

model = regressionModels$pid3

formula     =    model$formula
regex       =    names(model$data)
modelData   =    model$data

modelData   =    model$data %>%   
    data_grid(
      female  = mean(female) ,
      college = mean(college), 
      income  = mean(income),
      latino  = c(0, 1),
      married = mean(married),
      christian = mean(christian),
      gen_Boomer = mean(gen_Boomer),
      gen_Greatest = mean(gen_Greatest),
      gen_Millenial = mean(gen_Millenial),
      authM3 = seq(0, 1, by = 0.1)) %>%
    add_epred_draws(model) %>%
    mutate(latino = as.character(ifelse(latino == 0, "Non Hispanic White", "Latino"))) 
head(modelData)  
```

The data were generated using the `data_grid` function. The data are then used to generate the posterior estimates for the model. 


A simple comparison. Create a high, low, and middle value for authoritarianism. Then calculate the proportion of Latino's who are also authoritarian and Democrat. Likewise, calculate the proportion of non Hispanic Whites who are authoritarian and Democrat. Compare

Authoritarianism is more clearly aligned with partisanship among non Hispanic Whites. These effects are far more striking than the policy items. It suggests that authoritarianism has not been mapped onto party identification among Latinos. Put another way, proportionately more Latino authoritarians should identify as Democrat, relative to non Hispanic White authoritarians.

```{r}
#We can see this in a relatively simple comparison. Create a high, low, and middle value for authoritarianism. Then calculate the proportion of Latino's who are also authoritarian and Democrat. Likewise, calculate the proportion of non Hispanic Whites who are authoritarian and Democrat. Compare
compare = modDat %>%
  mutate(authM3 = cut(authM3, breaks = c(0, 0.33, 0.66, 1), labels = c("low", "middle", "high"))) 

prop.table(table(compare$authM3,  compare$party3, compare$latino), 2) %>% print()
```

If one is a latino and high on authoritarianism there is a 20% probability of identifying as Democrat. If one is a a non Hispanic White and high on authoritarianism there is a 8% probability of identifying as a Democrat. The inverse also holds. If one is a Latino and low on authoritarianism there is a 14% probability of identifying as a Republican. If one is a non Hispanic White and low on authoritarianism there is a 32% probability of identifying as a Republican.

Let's also calculate the marginal effect of authoritarianism on party identification. This is be done much the same as the most important problem item, the primary difference being there are only two categories. After doing this one final time, I'll create a general function that 1) constructs the data appropriately, and 2) calculate the model predictions and plot the results. 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyr)
library(dplyr)

xvar = "authM3"
mvar = "latino"
model = regressionModels$pid3

plotDat = posterior_means(model = model) %>%
  mutate(latino = as.factor(ifelse(latino == 0, "Non Hispanic White", "Latino"))) %>%
  mutate(.category = case_when(
    as.numeric(.category) == 1 ~ "Democrat",
    as.numeric(.category) == 2 ~ "Independent",
    as.numeric(.category) == 3 ~ "Republican",
    TRUE ~ NA
  ) ) 

plot1 = ggPoint(plotDat, nrow = 1)

```

*posterior_means* will calculate the posterior predictions for a model. *ggPoint* is a ggplot wrapper to plot the predictive effects. The functions can be used with nominal, ordinal, binary, and continuous dependent variables. And here is a a general function to create the marginal effects.

```{r}
posterior_pme(model) %>% head(12)
```


```{r}

plotData = posterior_pme(model = model) %>%
  mutate(latino = as.factor(ifelse(latino == 0, "Non Hispanic White", "Latino"))) %>%
  mutate(.category = case_when(
    as.numeric(.category) == 1 ~ "Democrat",
    as.numeric(.category) == 2 ~ "Independent",
    as.numeric(.category) == 3 ~ "Republican",
    TRUE ~ NA
  ) ) %>%  
  mutate(.category = factor(.category, levels = c("Democrat", "Independent", "Republican"))) 

plot1 +  ggMargins_categorical(plotData, nrow = 1, ylimits = c(-1, 1)) + 
  plot_layout(heights = c(2, 1), widths = c(2.5, 1))

```

Even though authoritarianism is expressed similarly in terms of policy, authoritarianism is far more electorally consequential among non Hispanic Whites. The marginal effect is much larger.  It's a similar story for voting. Authoritarianism shapes voting behavior more among non Hispanic Whites. 


```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 9}}
#names(regressionModels)

mvar = "latino"
model = regressionModels$trump2016

plot1 = posterior_means(model = model) %>%
  mutate(latino = as.factor(ifelse(latino == 0, "Non Hispanic White", "Latino")))  %>%
  ggPoint(nrow = 1, title = "Voting (Trump, 2016)", caption = "")  


plot2 = posterior_pme(model = model) %>%
  mutate(latino = as.factor(ifelse(latino == 0, "Non Hispanic White", "Latino")))  %>%
  ggMargins_nc(nrow = 1, ylimits = c(-1, 1)) 

model = regressionModels$trump2020

plot3 = posterior_means(model = model) %>%
  mutate(latino = as.factor(ifelse(latino == 0, "Non Hispanic White", "Latino")))  %>%
  ggPoint(nrow = 1, title = "2020")  


plot4 = posterior_pme(model = model) %>%
  mutate(latino = as.factor(ifelse(latino == 0, "Non Hispanic White", "Latino")))  %>%
  ggMargins_nc(nrow = 1, ylimits = c(-1, 1)) 


(plot1 + plot2) /(plot3 + plot4) 

names(regressionModels)
```
Finally, let's plot the 

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 9}}
items <- read.csv(paste0(getwd(), "/helper/itemType.csv")) 
  
models = regressionModels[names(regressionModels) %in% items$question]
nameModel = names(models)
# Create a vector of variables not yet analyzed in this names(regressionModels)

process_posterior <- function(model_data, recoder = "support5") {
  model_data %>%
    mutate(latino = as.factor(ifelse(latino == 0, "Non Hispanic White", "Latino"))) %>%
    mutate(.category = case_when(
      # recoder = support
      recoder == "support5" &  as.numeric(.category) == 5 ~ "Strongly Support",
      recoder == "support5" &  as.numeric(.category) == 4 ~ "Somewhat Support",
      recoder == "support5" &  as.numeric(.category) == 3 ~ "Neither Support nor Oppose",
      recoder == "support5" &  as.numeric(.category) == 2 ~ "Somewhat Oppose",
      recoder == "support5" &  as.numeric(.category) == 1 ~ "Strongly Oppose",
      recoder == "serious4" &  as.numeric(.category) == 4 ~ "Extremely Serious",
      recoder == "serious4" &  as.numeric(.category) == 3 ~ "A very serious problem",
      recoder == "serious4" &  as.numeric(.category) == 2 ~ "Somewhat serious",
      recoder == "serious4" &  as.numeric(.category) == 1 ~ "Not a problem",
      TRUE ~ NA
    )) 
}

 form = models[[1]]$formula 
 
# Parse this  in a regex to extrac the first element "immUndocumented ~ female + latino"

a1 <- posterior_pme(model = models[[1]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "immUndocumented")
a2 <- posterior_pme(model = models[[2]])  %>% process_posterior(recoder = "support5") %>% mutate(type = "immSeparation")
a3 <- posterior_pme(model = models[[3]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "immAsylum")
a4 <- posterior_pme(model = models[[4]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "immBirthright")
a5 <- posterior_pme(model = models[[5]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "immTech")
a6 <- posterior_pme(model = models[[6]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "immWall")
a7 <- posterior_pme(model = models[[6]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "concealCarry")
a8 <- posterior_pme(model = models[[7]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "background")
a9 <- posterior_pme(model = models[[8]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "registry")
a10 <- posterior_pme(model = models[[10]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "waterDams")
a11 <- posterior_pme(model = models[[11]]) %>% process_posterior(recoder = "serious4") %>% mutate(type = "envWater")
a12 <- posterior_pme(model = models[[12]]) %>% process_posterior(recoder = "support5") %>% mutate(type = "waterConservation")


```
